Model LF

### 2022-10-18 Inflation_model_updated.Rmd
Commit

---
title: "Model LF"
author: "Simon"
date: "11/7/2022"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

@@

```{r}
u=yk/(bd_nfc_k+equip_nfc_k) #Rate of capacity utilization
prate=s_nf/(stats::lag(bd_nfc,-1)+stats::lag(equip_nfc,-1)) # Profit rate
```

@@

```{r}
nl_check= (nl_h + nl_f + nl_nf + nl_g + nl_row) # needs to be fixed:
 fnl_check= (fnl_h + fnl_f + fnl_nf + fnl_g + fnl_row)  # this one is fine: because there is almost no connection between the real side and financial side at the moment
 check_np = np_row + np_h + np_f + np_nf + np_g # this one is fine:
 check_ctr = ctr_row + ctr_h + ctr_f + ctr_nf + ctr_g # this one is fine:
 check_invest = i - i_f - i_nf - i_g - i_h # this one is fine:
 check_iba = iba_h + iba_f + iba_nf + iba_g + iba_row  #needs to be fixed:
 check_tax = tax_g + tax_nf + tax_f + tax_h + tax_row # this one is fine:
  check_iba_rv = iba_h_rv + iba_f_rv + iba_nf_rv + iba_g_rv + iba_row_rv 
  check_iba_tr = iba_h_tr + iba_f_tr + iba_nf_tr + iba_g_tr + iba_row_tr
 check_eq = eq_h + (eq_f_a - eq_f_l) + (eq_nf_a - eq_nf_l) + eq_g + (eq_row_a - eq_row_l) # This one is now fixed
 check_eq_tr = eq_h_tr + Neq_nf_tr  + Neq_f_tr + eq_g_tr + Neq_row_tr + eq_g_tr
  check_l = l_h + l_f + l_nf + l_g + l_row # problematic after scenario 2
 check_l_tr = l_f_tr + l_h_tr + l_nf_tr + l_g_tr + l_row_tr
  check_ins = ins_h + ins_f + ins_nf + ins_g + ins_row # problematic after scenario 2
 check_ins_tr =  ins_f_tr  + ins_h_tr + ins_nf_tr + ins_g_tr + ins_row_tr
check_sec = sec_h + sec_f_a + sec_f_d + sec_nf + sec_g + sec_row ## needs to be fixed
```

@@

yk_ds=ts(yk_ds,start = c(2005,2), end = c(2020,1), frequency = 4 )

@@

## Shock_1
pf_shock= pf+pf*0.1
pm_ds_shock= pm_ds+pm_ds*0.1

@@

tax_rate1_shock= ts(c(0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369), start = c(2005, 2), end =  c(2020,1), frequency = 4)

## shock g
g_shock= g*1.02

@@

shock_g_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_1_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_2_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_3_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

@@

COMMENT> 
BEHAVIORAL> i_equip_nfc_k_ds
TSRANGE 2006 1 2020 1
EQ> LOG(i_equip_nfc_k_ds) = p_807 + p_808 * TSDELTALOG(TSLAG(i_equip_nfc_k_ds,1)/TSLAG(equip_nfc_k,2)) + p_809 * TSDELTALOG(ps_ds) + p_810 * TSDELTALOG(u_ds) + p_811 *  LOG(TSLAG(i_equip_nfc_k_ds,1)/TSLAG(equip_nfc_k,2)) + p_812 * LOG(TSLAG(ps_ds,1)) + p_813 * LOG(TSLAG(u_ds,1)) + p_814 * dummy_10 + p_815 * dummy_11 + p_890*TSDELTALOG(tobinq) + p_891*LOG(TSLAG(tobinq,1)) + alpha_1*TSLAG(LOG(i_equip_nfc_k_ds),1) + alpha_2*TSLAG(LOG(equip_nfc_k),1) + alpha_3*TSLAG(-LOG(equip_nfc_k),2)
COEFF> p_807 p_808 p_809 p_810 p_811 p_812 p_813 p_814 p_815 p_890 p_891 alpha_1 alpha_2 alpha_3
RESTRICT> alpha_1 = 1
alpha_2 = 1
alpha_3 = 1
STORE> coe(11)

@@

COMMENT> 
BEHAVIORAL> pc_ds
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(pc_ds) = C_21*TSDELTALOG(TSLAG(pc_ds,1)) + C_22*TSDELTALOG(TSLAG(pc_ds,2))+ C_23*TSDELTALOG(TSLAG(pc_ds,3)) + C_24*TSDELTALOG(TSLAG(pc_ds,4)) + C_25*TSDELTALOG(wage_ds)+ C_26*TSDELTALOG(pm_ds) + C_27*TSDELTALOG(TSLAG(pm_ds,2)) + C_28*LOG(TSLAG(pc_ds,1)) + C_29*LOG(TSLAG(wage_ds,1)) + C_30*LOG(TSLAG(prod_ds,1)) + C_31*LOG(TSLAG(pm_ds,1)) + C_32* d_2007q3 + C_33*d_2017q3+ C_34* d_2018q1 + C_35*d_2011q2 + C_36* d_2013q1 
COEFF> C_21 C_22 C_23 C_24 C_25 C_26 C_27 C_28 C_29 C_30 C_31 C_32 C_33 C_34 C_35 C_36
STORE> coe(12)

@@

COMMENT> Capital Stock with switches
IDENTITY> pf
EQ> pf = pf*1
IF> shock_1_model <= 0
IDENTITY> pf
EQ> pf = pf_shock
IF> shock_1_model > 0

COMMENT> Capital Stock with switches
IDENTITY> pm_ds
EQ> pm_ds = pm_ds*1
IF> shock_1_model <= 0
IDENTITY> pm_ds
EQ> pm_ds = pm_ds_shock
IF> shock_1_model > 0

COMMENT> Capital Stock with switches
IDENTITY> iloan
EQ> iloan = iloan*1
IF> shock_2_model <= 0
IDENTITY> iloan
EQ> iloan = iloan_shock
IF> shock_2_model > 0

@@

COMMENT> Capital Stock with switches
IDENTITY> g
EQ> g = g*1
IF> shock_g_model <= 0
IDENTITY> g
EQ> g = g_shock
IF> shock_g_model > 0

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_g_model
EQ> shock_g_model = shock_g_model*1

@@

  ws = TIMESERIES(c(ws),   
                  START=c(2005,2),FREQ=4),
  ps = TIMESERIES(c(ps),   
                  START=c(2005,2),FREQ=4),
  u = TIMESERIES(c(u),   
                 START=c(2005,2),FREQ=4),
  prate = TIMESERIES(c(prate),   
                     START=c(2005,3),FREQ=4),
  tobinq = TIMESERIES(c(tobinq),   
                      START=c(2005,2),FREQ=4),

@@

  prod = TIMESERIES(c(prod),   
                    START=c(2005,2),FREQ=4),
  acc_rate = TIMESERIES(c(acc_rate),   
                        START=c(2005,2),FREQ=4),
  shock = TIMESERIES(c(shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),

@@

@@

  oecd = TIMESERIES(c(oecd),   
                    START=c(2005,2),FREQ=4),
  oecde = TIMESERIES(c(oecde),   
                     START=c(2005,2),FREQ=4),

  g_20 = TIMESERIES(c(g_20),   
                    START=c(2005,2),FREQ=4),
  ea19 = TIMESERIES(c(ea19),   
                    START=c(2005,2),FREQ=4),
  eu = TIMESERIES(c(eu),   
                  START=c(2005,2),FREQ=4),
  gdp_tp = TIMESERIES(c(gdp_tp),   
                      START=c(2005,2),FREQ=4),
  rer_old = TIMESERIES(c(rer_old),   
                       START=c(2005,2),FREQ=4),
  xr = TIMESERIES(c(xr),   
                  START=c(2005,2),FREQ=4),
  p_trade = TIMESERIES(c(p_trade),   
                       START=c(2005,2),FREQ=4),

@@

  empadj = TIMESERIES(c(empadj),   
                        START=c(2005,2),FREQ=4),
  part = TIMESERIES(c(part),   
                         START=c(2005,2),FREQ=4),
  pop = TIMESERIES(c(pop),   
                           START=c(2005,2),FREQ=4),
  urs = TIMESERIES(c(urs),   
                            START=c(2005,2),FREQ=4),
  wage_2010q3 = TIMESERIES(c(wage_2010q3),   
                              START=c(2005,2),FREQ=4),
  neq_nf_rvx = TIMESERIES(c(Neq_nf_rvx),   
                           START=c(2005,3),FREQ=4),
  eq_h_f_rvx = TIMESERIES(c(eq_h_f_rvx),   
                           START=c(2005,3),FREQ=4),
  g = TIMESERIES(c(g),   
                           START=c(2005,2),FREQ=4),
  pg = TIMESERIES(c(pg),   
                           START=c(2005,2),FREQ=4),
  px = TIMESERIES(c(px),   
                           START=c(2005,2),FREQ=4),
  pf = TIMESERIES(c(pf),   
                           START=c(2005,2),FREQ=4),
  pm = TIMESERIES(c(pm),   
                           START=c(2005,2),FREQ=4),
  div_nf_adj = TIMESERIES(c(div_nf_adj),   
                           START=c(2005,3),FREQ=4),
  ins_nf_adj = TIMESERIES(c(ins_nf_adj),   
                           START=c(2005,3),FREQ=4),
  res_p_nf = TIMESERIES(c(res_p_nf),   
                           START=c(2005,2),FREQ=4),
  res_r_nf = TIMESERIES(c(res_r_nf),   
                           START=c(2005,2),FREQ=4),
  int_r_f = TIMESERIES(c(int_r_f),   
                           START=c(2005,2),FREQ=4),
  np_f = TIMESERIES(c(np_f),   
                           START=c(2005,2),FREQ=4),
  np_g = TIMESERIES(c(np_g),   
                           START=c(2005,2),FREQ=4),
  eq_g_nf_rv = TIMESERIES(c(eq_g_nf_rv),   
                           START=c(2005,2),FREQ=4),
  prodk = TIMESERIES(c(prodk),   
                           START=c(2005,2),FREQ=4),

@@

  ## Test
  tax_rate1_shock  = TIMESERIES(c(tax_rate1_shock ),   
                           START=c(2005,2),FREQ=4),
  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_g_model  = TIMESERIES(c(shock_g_model),   
                           START=c(2005,2),FREQ=4),

@@

# Estimate
```{r}

@@

# Simulate 
```{r}
# In-sample prediction (no add factors)
S_model <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                   )
```

### compare with real data

```{r, echo=FALSE}
### Gengivelse
yk_ds_00 = S_model$simulation$yk_ds
emp_00 = S_model$simulation$emp
wage_ds_00 = S_model$simulation$wage_ds
ik_00 = S_model$simulation$ik
pc_ds_00 = S_model$simulation$pc_ds
yd_hk_ds_00 = S_model$simulation$yd_hk_ds 
pconk_ds_00 = S_model$simulation$pconk_ds 
ur_ds_00 = S_model$simulation$ur_ds
tax_rate1_00 = S_model$simulation$tax_rate1
iloan_00 = S_model$simulation$iloan
iboa_00 = S_model$simulation$iboa
pf_00 = S_model$simulation$pf

yd1_h_00 = S_model$simulation$yd1_h
g_00 = S_model$simulation$g

@@

### Gengivelse
plot(wage_ds_00, col= "green"); lines(wage_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

>>>>

---
title: "Model LF"
author: "Simon"
date: "11/7/2022"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

@@

@@

```{r, echo=FALSE}
nl_check= (nl_h + nl_f + nl_nf + nl_g + nl_row) # needs to be fixed:
 fnl_check= (fnl_h + fnl_f + fnl_nf + fnl_g + fnl_row)  # this one is fine: because there is almost no connection between the real side and financial side at the moment
 check_np = np_row + np_h + np_f + np_nf + np_g # this one is fine:
 check_ctr = ctr_row + ctr_h + ctr_f + ctr_nf + ctr_g # this one is fine:
 check_invest = i - i_f - i_nf - i_g - i_h # this one is fine:
 check_iba = iba_h + iba_f + iba_nf + iba_g + iba_row  #needs to be fixed:
 check_tax = tax_g + tax_nf + tax_f + tax_h + tax_row # this one is fine:
  check_iba_rv = iba_h_rv + iba_f_rv + iba_nf_rv + iba_g_rv + iba_row_rv 
  check_iba_tr = iba_h_tr + iba_f_tr + iba_nf_tr + iba_g_tr + iba_row_tr
 check_eq = eq_h + (eq_f_a - eq_f_l) + (eq_nf_a - eq_nf_l) + eq_g + (eq_row_a - eq_row_l) # This one is now fixed
 check_eq_tr = eq_h_tr + Neq_nf_tr  + Neq_f_tr + eq_g_tr + Neq_row_tr + eq_g_tr
  check_l = l_h + l_f + l_nf + l_g + l_row # problematic after scenario 2
 check_l_tr = l_f_tr + l_h_tr + l_nf_tr + l_g_tr + l_row_tr
  check_ins = ins_h + ins_f + ins_nf + ins_g + ins_row # problematic after scenario 2
 check_ins_tr =  ins_f_tr  + ins_h_tr + ins_nf_tr + ins_g_tr + ins_row_tr
check_sec = sec_h + sec_f_a + sec_f_d + sec_nf + sec_g + sec_row ## needs to be fixed
```

@@

yk_ds=ts(yk_ds,start = c(2005,2), end = c(2020,1), frequency = 4)
u_ds=yk_ds/(bd_nfc_k+equip_nfc_k) #Rate of capacity utilization

lambda <- 1600
hp = hpfilter(yk_ds, lambda)
yk_ds_potential <- hp$trend

yk_ds_potential=ts(yk_ds_potential, start = c(2005,2), end = c(2020,1), frequency = 4 )

prate=s_nf/(stats::lag(bd_nfc,-1)+stats::lag(equip_nfc,-1)) # Profit rate

@@

## Shock_1
pf_shock= pf+pf*0.1
pm_ds_shock= pm_ds+pm_ds*0.1
p_expect_shock = p_expect + 30 # it went up during covid-19 from 20 to 60 points so, introduce 30 points increase here
gdp_tp_shock = gdp_tp*(1- 0.025)
yk_ds_potential_shock = yk_ds_potential*(1-0.015)

@@

tax_rate1_shock = tax_rate1 - 0.02

@@

shock_1_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_2_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_3_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

```{r, echo=FALSE}

@@

COMMENT> 
BEHAVIORAL> i_equip_nfc_k_ds
TSRANGE 2006 1 2020 1
EQ> LOG(i_equip_nfc_k_ds) = p_809 + p_810 * TSDELTALOG(TSLAG(i_equip_nfc_k_ds,1)/TSLAG(equip_nfc_k,2)) + p_811 *  LOG(TSLAG(i_equip_nfc_k_ds,1)/TSLAG(equip_nfc_k,2)) + p_812 * LOG(TSLAG(ps_ds,1)) + p_813 * LOG(TSLAG(u_ds,1)) + p_814 * dummy_10 + p_815 * dummy_11 + p_816*TSDELTALOG(tobinq) + p_817*LOG(TSLAG(tobinq,1)) + alpha_1*TSLAG(LOG(i_equip_nfc_k_ds),1) + alpha_2*TSLAG(LOG(equip_nfc_k),1) + alpha_3*TSLAG(-LOG(equip_nfc_k),2)
COEFF> p_809 p_810 p_811 p_812 p_813 p_814 p_815 p_816 p_817 alpha_1 alpha_2 alpha_3
RESTRICT> alpha_1 = 1
alpha_2 = 1
alpha_3 = 1
STORE> coe(11)

@@

COMMENT> 
BEHAVIORAL> pc_ds
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(pc_ds) = C_21*TSDELTALOG(TSLAG(pc_ds,1)) + C_22*TSDELTALOG(TSLAG(pc_ds,2))+ C_23*TSDELTALOG(TSLAG(pc_ds,3)) + C_24*TSDELTALOG(TSLAG(pc_ds,4)) + C_25*TSDELTALOG(wage_ds)+ C_26*TSDELTALOG(pm_ds) + C_27*TSDELTALOG(TSLAG(pm_ds,2)) + C_28*LOG(TSLAG(pc_ds,1)) + C_29*LOG(TSLAG(wage_ds,1)) + C_30*LOG(TSLAG(prod_ds,1)) + C_31*LOG(TSLAG(pm_ds,1)) + C_32* d_2007q3 + C_33*d_2017q23 + C_34*d_2018q1 + C_35*d_2011q2  + C_36*d_2013q1 + C_37*(yk_ds_potential -  (pconk_ds + ik + gk)) +  C_38*TSDELTA(p_expect)

COEFF> C_21 C_22 C_23 C_24 C_25 C_26 C_27 C_28 C_29 C_30 C_31 C_32 C_33 C_34 C_35 C_36 C_37  C_38 
STORE> coe(12)

@@

COMMENT> Variables for Shock 1 activation
IDENTITY> pf
EQ> pf = pf*1
IF> shock_1_model <= 0
IDENTITY> pf
EQ> pf = pf_shock
IF> shock_1_model > 0

COMMENT> Variables for Shock 1 activation
IDENTITY> pm_ds
EQ> pm_ds = pm_ds*1
IF> shock_1_model <= 0
IDENTITY> pm_ds
EQ> pm_ds = pm_ds_shock
IF> shock_1_model > 0

COMMENT> Variables for Shock 1 activation
IDENTITY> p_expect
EQ> p_expect = p_expect*1
IF> shock_1_model <= 0
IDENTITY> p_expect
EQ> p_expect = p_expect_shock
IF> shock_1_model > 0

COMMENT> Variables for Shock 1 activation
IDENTITY> gdp_tp
EQ> gdp_tp = gdp_tp*1
IF> shock_1_model <= 0
IDENTITY> gdp_tp
EQ> gdp_tp = gdp_tp_shock
IF> shock_1_model > 0

COMMENT> Variables for Shock 1 activation
IDENTITY> yk_ds_potential
EQ>  yk_ds_potential =  yk_ds_potential*1
IF> shock_1_model <= 0
IDENTITY>  yk_ds_potential
EQ>  yk_ds_potential =  yk_ds_potential_shock
IF> shock_1_model > 0

COMMENT> Variables for Shock 1 activation
IDENTITY> iloan
EQ> iloan = iloan*1
IF> shock_2_model <= 0
IDENTITY> iloan
EQ> iloan = iloan_shock
IF> shock_2_model > 0

@@

@@

  ws = TIMESERIES(c(ws),   
                  START=c(2005,2),FREQ=4),
  ps = TIMESERIES(c(ps),   
                  START=c(2005,2),FREQ=4),

  prate = TIMESERIES(c(prate),   
                     START=c(2005,3),FREQ=4),
  tobinq = TIMESERIES(c(tobinq),   
                      START=c(2005,2),FREQ=4),

@@

  prod = TIMESERIES(c(prod),   
                    START=c(2005,2),FREQ=4),
  acc_rate = TIMESERIES(c(acc_rate),   
                        START=c(2005,2),FREQ=4),
  shock = TIMESERIES(c(shock),   
                        START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  p_expect_shock = TIMESERIES(c(p_expect_shock),   
                        START=c(2005,2),FREQ=4),
  yk_ds_potential_shock = TIMESERIES(c(yk_ds_potential_shock),   
                        START=c(2005,2),FREQ=4),
  gdp_tp_shock = TIMESERIES(c(gdp_tp_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),

@@

  yk_ds_potential= TIMESERIES(c(yk_ds_potential),   
                     START=c(2005,2),FREQ=4),

@@

  oecd = TIMESERIES(c(oecd),   
                    START=c(2005,2),FREQ=4),
  oecde = TIMESERIES(c(oecde),   
                     START=c(2005,2),FREQ=4),
  g_20 = TIMESERIES(c(g_20),   
                    START=c(2005,2),FREQ=4),
  ea19 = TIMESERIES(c(ea19),   
                    START=c(2005,2),FREQ=4),
  eu = TIMESERIES(c(eu),   
                  START=c(2005,2),FREQ=4),
  gdp_tp = TIMESERIES(c(gdp_tp),   
                      START=c(2005,2),FREQ=4),
  rer_old = TIMESERIES(c(rer_old),   
                       START=c(2005,2),FREQ=4),
  xr = TIMESERIES(c(xr),   
                  START=c(2005,2),FREQ=4),
  p_trade = TIMESERIES(c(p_trade),   
                       START=c(2005,2),FREQ=4),

@@

  empadj = TIMESERIES(c(empadj),   
                        START=c(2005,2),FREQ=4),
  part = TIMESERIES(c(part),   
                         START=c(2005,2),FREQ=4),
  pop = TIMESERIES(c(pop),   
                           START=c(2005,2),FREQ=4),
  urs = TIMESERIES(c(urs),   
                            START=c(2005,2),FREQ=4),
  wage_2010q3 = TIMESERIES(c(wage_2010q3),   
                              START=c(2005,2),FREQ=4),
  neq_nf_rvx = TIMESERIES(c(Neq_nf_rvx),   
                           START=c(2005,3),FREQ=4),
  eq_h_f_rvx = TIMESERIES(c(eq_h_f_rvx),   
                           START=c(2005,3),FREQ=4),
  g = TIMESERIES(c(g),   
                           START=c(2005,2),FREQ=4),
  pg = TIMESERIES(c(pg),   
                           START=c(2005,2),FREQ=4),
  px = TIMESERIES(c(px),   
                           START=c(2005,2),FREQ=4),
  pf = TIMESERIES(c(pf),   
                           START=c(2005,2),FREQ=4),
  p_expect = TIMESERIES(c(p_expect),   
                           START=c(2005,2),FREQ=4),
  pm = TIMESERIES(c(pm),   
                           START=c(2005,2),FREQ=4),
  div_nf_adj = TIMESERIES(c(div_nf_adj),   
                           START=c(2005,3),FREQ=4),
  ins_nf_adj = TIMESERIES(c(ins_nf_adj),   
                           START=c(2005,3),FREQ=4),
  res_p_nf = TIMESERIES(c(res_p_nf),   
                           START=c(2005,2),FREQ=4),
  res_r_nf = TIMESERIES(c(res_r_nf),   
                           START=c(2005,2),FREQ=4),
  int_r_f = TIMESERIES(c(int_r_f),   
                           START=c(2005,2),FREQ=4),
  np_f = TIMESERIES(c(np_f),   
                           START=c(2005,2),FREQ=4),
  np_g = TIMESERIES(c(np_g),   
                           START=c(2005,2),FREQ=4),
  eq_g_nf_rv = TIMESERIES(c(eq_g_nf_rv),   
                           START=c(2005,2),FREQ=4),
  prodk = TIMESERIES(c(prodk),   
                           START=c(2005,2),FREQ=4),

@@

  ## Test
  tax_rate1_shock  = TIMESERIES(c(tax_rate1_shock ),   
                           START=c(2005,2),FREQ=4),
  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),

@@

# Estimations
```{r}

@@

# Baseline Simulations
```{r, results='hide'}
# In-sample prediction (no add factors)
S_model <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                   )
```

```{r}
shock_1_model_shock = shock_1_model %>% window(start= c(2014,2))
```

```{r}
constantAdjList <- list(
 shock_1_model = TIMESERIES(shock_1_model_shock+1 ,START=c(2014,2),  FREQ='Q')
 )

```{r, results='hide'}
# Simulate the model (following shock)
Shock_1 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList
                    )
```

## Scenario 1 + 2

```{r}
shock_2_model_shock=shock_2_model %>% window(start= c(2014,4))
```

  shock_1_model = TIMESERIES(shock_1_model_shock+1 ,START=c(2014,2),  FREQ='Q'),
  shock_2_model = TIMESERIES(shock_2_model_shock+1 ,START=c(2014,4),  FREQ='Q')
  )

```{r, results='hide'}
# Simulate the model (following shock)
Shock_2 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_1
                    )
```

# Secnario 1 + 2 + 3

```{r}
shock_3_model_shock = shock_3_model %>% window(start= c(2014,2))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_2 <- list(
  shock_1_model = TIMESERIES(shock_1_model_shock+1 ,START=c(2014,2),  FREQ='Q'),
  shock_2_model = TIMESERIES(shock_2_model_shock+1 ,START=c(2014,4),  FREQ='Q'),
  shock_3_model = TIMESERIES(shock_3_model_shock+1 ,START=c(2014,4),  FREQ='Q')
 )
```

```{r, results='hide'}
# Simulate the model (following shock)
Shock_3 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_2
                    )
```

# Extract key variables

@@

# Baseline 
yk_ds_00 = S_model$simulation$yk_ds;         yk_ds_0 <- window(yk_ds_00, start=c(2012,1), freq=4)
emp_00 = S_model$simulation$emp
wage_ds_00 = S_model$simulation$wage_ds
rw_ds_00=S_model$simulation$rw_ds;            rw_ds_0 <- window(rw_ds_00, start=c(2012,1), freq=4)
ik_00 = S_model$simulation$ik;       ik_0 <- window(ik_00, start=c(2012,1), freq=4)
i_bd_nfc_k_ds_00 = S_model$simulation$i_bd_nfc_k_ds
i_bd_h_k_ds_00 = S_model$simulation$i_bd_h_k_ds
i_equip_nfc_k_ds_00 = S_model$simulation$i_equip_nfc_k_ds
i_equip_h_k_ds_00 = S_model$simulation$i_equip_h_k_ds
pc_ds_00 = S_model$simulation$pc_ds;         pc_ds_0 <- window(pc_ds_00, start=c(2012,1), freq=4)
yd_hk_ds_00 = S_model$simulation$yd_hk_ds 
pconk_ds_00 = S_model$simulation$pconk_ds;       pconk_ds_0 <- window(pconk_ds_00, start=c(2012,1), freq=4)
ur_ds_00 = S_model$simulation$ur_ds   ;         ur_ds_0 <- window(ur_ds_00, start=c(2012,1), freq=4) 
tax_rate1_00 = S_model$simulation$tax_rate1
iloan_00 = S_model$simulation$iloan
iboa_00 = S_model$simulation$iboa
pm_ds_00 = S_model$simulation$pm_ds
yk_ds_potential_00 = S_model$simulation$yk_ds_potential
gdp_tp_00= S_model$simulation$gdp_tp
pf_00 = S_model$simulation$pf
p_expect_00 = S_model$simulation$p_expect
inflation_t_00= S_model$simulation$inflation_t
inflation_00= S_model$simulation$inflation;           inflation_0 <- window(inflation_00, start=c(2012,1), freq=4)
rer_00= S_model$simulation$rer;    rer_0 <- window(rer_00, start=c(2012,1), freq=4)
eq_h_00 = S_model$simulation$eq_h
l_h_00 = S_model$simulation$l_h
l_h_tr_00 = S_model$simulation$l_h_tr
xk_ds_00= S_model$simulation$xk_ds;         xk_ds_0 <- window(xk_ds_00, start=c(2012,1), freq=4)
mk_ds_00= S_model$simulation$mk_ds;         mk_ds_0 <- window(mk_ds_00, start=c(2012,1), freq=4)
yd1_h_00 = S_model$simulation$yd1_h
nl_g_00 <- S_model$simulation$nl_g;  nl_g_0 <- window(nl_g_00, start=c(2012,1), freq=4)

fnw_g_00 <- S_model$simulation$fnw_g; fnw_g_0 <- window(fnw_g_00, start=c(2012,1), freq=4)

y_00 <- S_model$simulation$y;  y_0 <- window(y_00, start=c(2012,1), freq=4)

# Scenario 1 variables
yk_ds_01 = Shock_1$simulation$yk_ds;           yk_ds_1 <- window(yk_ds_01, start=c(2012,1), freq=4)

y_01 = Shock_1$simulation$y;           y_1 <- window(y_01, start=c(2012,1), freq=4)
emp_01 = Shock_1$simulation$emp
wage_ds_01 = Shock_1$simulation$wage_ds
rw_ds_01=Shock_1$simulation$rw_ds;             rw_ds_1 <- window(rw_ds_01, start=c(2012,1), freq=4)
ur_ds_01 = Shock_1$simulation$ur_ds;           ur_ds_1 <- window(ur_ds_01, start=c(2012,1), freq=4)
pc_ds_01 = Shock_1$simulation$pc_ds;           pc_ds_1 <- window(pc_ds_01, start=c(2012,1), freq=4)
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
pconk_ds_01 = Shock_1$simulation$pconk_ds;       pconk_ds_1 <- window(pconk_ds_01, start=c(2012,1), freq=4)
ik_01 = Shock_1$simulation$ik   ;                ik_1 <- window(ik_01, start=c(2012,1), freq=4)
inflation_01 = Shock_1$simulation$inflation;     inflation_1 <- window(inflation_01, start=c(2012,1), freq=4)
inflation_t_01= Shock_1$simulation$inflation_t
eq_h_01 = Shock_1$simulation$eq_h
l_h_01 = Shock_1$simulation$l_h
l_h_tr_01 = Shock_1$simulation$l_h_tr
rer_01= Shock_1$simulation$rer;                   rer_1 <- window(rer_01, start=c(2012,1), freq=4)
xk_ds_01= Shock_1$simulation$xk_ds  ;               xk_ds_1 <- window(xk_ds_01, start=c(2012,1), freq=4)
mk_ds_01= Shock_1$simulation$mk_ds;                 mk_ds_1 <- window(mk_ds_01, start=c(2012,1), freq=4)
i_bd_nfc_k_ds_01 = Shock_1$simulation$i_bd_nfc_k_ds
i_bd_h_k_ds_01 = Shock_1$simulation$i_bd_h_k_ds
i_equip_nfc_k_ds_01 = Shock_1$simulation$i_equip_nfc_k_ds
i_equip_h_k_ds_01 = Shock_1$simulation$i_equip_h_k_ds
nl_g_01 <- Shock_1$simulation$nl_g;  nl_g_1 <- window(nl_g_01, start=c(2012,1), freq=4)
fnw_g_01 <- Shock_1$simulation$fnw_g; fnw_g_1 <- window(fnw_g_01, start=c(2012,1), freq=4)

# Scenario 1 + 2 variables
